---
title: "sm_rnp_f_u_length"
output: html_document
date: "2024-08-05"
---

```{r}
library(tidyverse)
library(readxl)
```

## Import data

Import all follow-up length dataset and separate to 3 groups

```{r}
followup_df = read_excel("./r-sm-rnp.xlsx") %>% 
  janitor::clean_names() %>% 
  select(group, follow_up_length)

followup1_df = followup_df = read_excel("./r-sm-rnp.xlsx") %>% 
  janitor::clean_names() %>% 
  select(group, follow_up_length) %>% 
  filter(group == 1)

followup2_df = followup_df = read_excel("./r-sm-rnp.xlsx") %>% 
  janitor::clean_names() %>% 
  select(group, follow_up_length) %>% 
  filter(group == 2)

followup3_df = followup_df = read_excel("./r-sm-rnp.xlsx") %>% 
  janitor::clean_names() %>% 
  select(group, follow_up_length) %>% 
  filter(group == 3)
```

## Check distribution

```{r}
skimr::skim(followup_df)

skimr::skim(followup1_df)

skimr::skim(followup2_df)

skimr::skim(followup3_df)
```

## Perform Mann Whitney U test

Perform Mann Whitney U test between double positive and Sm-RNP positive group

```{r}
followup1_df = followup_df = read_excel("./r-sm-rnp.xlsx") %>% 
  janitor::clean_names() %>% 
  select(group, follow_up_length) %>% 
  filter(group < 3)

result_dp_smrnp = wilcox.test(follow_up_length~group, followup1_df, exact = FALSE)
```

Perform Mann Whitney U test between double positive and RNP positive group

```{r}
followup2_df = followup_df = read_excel("./r-sm-rnp.xlsx") %>% 
  janitor::clean_names() %>% 
  select(group, follow_up_length) %>% 
  filter(group != 2)

result_dp_rnp = wilcox.test(follow_up_length~group, followup2_df, exact = FALSE)
```

Perform Mann Whitney U test between Sm-RNP and RNP positive group

```{r}
followup3_df = followup_df = read_excel("./r-sm-rnp.xlsx") %>% 
  janitor::clean_names() %>% 
  select(group, follow_up_length) %>% 
  filter(group != 1)

result_smrnp_rnp = wilcox.test(follow_up_length~group, followup3_df, exact = FALSE)
```

# Follow Up Length Comparison Between Two Groups

Comparison between double positive and Sm-RNP only
```{r}
result_dp_smrnp
```

Comparison between double positive and RNP only
```{r}
result_dp_rnp
```

Comparison between Sm-RNP and RNP only
```{r}
result_smrnp_rnp
```

